---
title: "Access GBADs Metadata"
author: "Kassy Raymond"
date: "2024-11-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Connect to Neo4j Aura using the GBADs API  

The purpose of this script is to use the GBADs Application Programming Interface (API) 
to get information about the metadata and data sources available in the 
Neo4j Graph Database instance. 

```{r}
# include packages for use
# install.packages(c("httr", "jsonlite"))
library(httr)
library(jsonlite)
```

```{r}
# Get a list of species available for query 
res = GET('https://gbadske.org/meta-api/species')
species = fromJSON(rawToChar(res$content))
species
```

Using this list of species, we can use them to query for data of interest. 
We also need countrys.

```{r}
# Get a list of countries available for query 
res = GET('https://gbadske.org/meta-api/countries')
countries = fromJSON(rawToChar(res$content))
countries
```

Using countries and species of interest, we can get data.

```{r}
res = GET('https://gbadske.org/meta-api/datasets?countries=Canada&species=Cattle')
data = fromJSON(rawToChar(res$content))
data
```
